A Review of Neutron Imaging

### 2020-10-12 neutron-imaging/neutron.tex
WIP 12Oct2020

\section{Imaging of biologically important structures}\label{s10}
\section{Larmor precession based imaging}\label{s11}
\section{Polarization based imaging}\label{s12}
\section{Conclusion}\label{s13}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}

>>>>

\section{Phase-contrast imaging}\label{s10}
When electromagnetic radiation passes from one medium to another it undergoes
both refraction and attenuation. The phenomena can be described together 
through the complex refractive index \cite{heald2012classical} where the
real part describes the refraction and the imaginary part the attenuation. 
The propagation of neutron beams through media too can be expressed by a 
complex refractive index. The 2-d imaging and the tomographic techniques
considered in the previous sections considered images acquired due to 
attenuation. In this section we shall briefly considered imaging due to phase
contrast. Equation \eqref{s7e3} indicated that the refractive index of neutrons
is less than $1$. Therefore, it is customary to express the complex refractive
index as
\begin{equation}\label{s10e1}
n(\vec{x}) = 1 - \delta(\vec{x}) + i\beta(\vec{x}),
\end{equation}
where the dependence on $\vec{x}$, the position in the medium, allows for the
inhomogeneous nature of the real and imaginary parts of the refractive index.
Aluminum and Silicon have very small values $\beta$. Therefore, they hardly
attenuate a neutron beam and cannot produce a 2-d image or a tomogram of 
sufficient contrast. On the other hand, their $\delta$ values are $5$ orders
of magnitude larger and can yield excellent phase-contrast images 
\cite{anderson2008neutron}. Titanium and Copper have very similar $\beta$
values and therefore cannot be differentiated by their attenuation properties.
Their $\delta$ values are of opposite signs. Titanium with $\delta=-5.0 \times
10^{-6}$ makes neutron beams behave somewhat like electromagnetic radiation
by making the real part of the refractive index slightly greater than one
\cite{anderson2008neutron}.

The phase differences caused by the real part of the refractive index are
detected by interference \cite{zawisky2004neutron}. A monochromatic beam of
neutrons is coherently split into a reference beam and an object beam. The 
object beam is passed through the target and suffers a phase shift (and 
attenuation). After it emerges from the target it is superposed with the 
reference beam. The interference between the two is captured in a digital
neutron camera.

Phase differences can either be recorded as a 2-d image or a tomogram. In the
latter case, the 3-d distribution of the refractive index of the target is 
reconstructed. The phase differences can either be represented as the 
differences in their values or the gradient of phase shift or the laplacian of
the phase shift \cite{anderson2008neutron}.

\section{Larmor precession based imaging}\label{s11}
\section{Polarization based imaging}\label{s12}
\section{Imaging of biologically important structures}\label{s13}
\section{Conclusion}\label{s14}
\bibliography{neutron}
\bibliographystyle{plain}
\end{document}
